COLLISION RATES OF PLANETESIMALS NEAR MEAN-MOTION RESONANCES

### 2019-08-22 main.tex
Outline figures to show

@@

>>>>

Outline for this section:
\begin{list}
\li Time evolution of disk surface density for circ and ecc
\li Time evolution of sma vs ecc
\li Number of collisions as a function of sma and radial distance
\li Number of collisions as a function of mean anomaly and delta mean anomaly
\li Comparison between safronov rate and actual collision statistics
\end{list}

@@

\begin{list}
\li Show CASA images
\end{list}
